### 2017-10-17 paper/sexSelectionSpacing-ver1.tex
Fix figure reference

The effect of sex selection on spacing first show up for urban women with
8 or more years of education.
Panel (a) in Figure \ref{fig:results_spell2_high_pps} show shorter spacing
for the second spell when the first child is a girl than a boy, and this
pattern is also present in Panel (b).
Panel (c) on the other hand show first evidence of \emph{longer} spacing 
after the birth of a girl than after a boy, consistent with the male-biased
sex ratio in Panel (c) in Figure \ref{fig:fig:results_spell2_high_urban}.

>>>>

The effect of sex selection on spacing first show up for urban women with
8 or more years of education.
Panel (a) in Figure \ref{fig:results_spell2_high_pps} show shorter spacing
for the second spell when the first child is a girl than a boy, and this
pattern is also present in Panel (b).
Panel (c) on the other hand show first evidence of \emph{longer} spacing 
after the birth of a girl than after a boy, consistent with the male-biased
sex ratio in Panel (c) in Figure \ref{fig:results_spell2_high_urban}.
